### 2024-01-12 ms.qmd
Updates

```{r, resultsAssodeli}

>>>>

```{r, resultsAsso}
# Rename some of the posteriors and make new estimates for the learning rate for the Associative task
## 1) L. delicata
### Group = red
d_a_r_CORTCold <- deli_asso_red$b_Associative_Trial #"Learning estimate" for treatment CORT-Cold for L. delicata, red as the right choice
d_a_r_ControlCold <- (deli_asso_red$'b_Associative_Trial:cortControl' + deli_asso_red$b_Associative_Trial)
d_a_r_CORTHot <- (deli_asso_red$'b_Associative_Trial:tempHot' + deli_asso_red$b_Associative_Trial)
d_a_r_ControlHot <- (deli_asso_red$'b_Associative_Trial:cortControl:tempHot' + deli_asso_red$b_Associative_Trial)
### Group = blue
d_a_b_CORTCold <- deli_asso_blue$b_Associative_Trial
d_a_b_ControlCold <- (deli_asso_blue$'b_Associative_Trial:cortControl' + deli_asso_blue$b_Associative_Trial)
d_a_b_CORTHot <- (deli_asso_blue$'b_Associative_Trial:tempHot' + deli_asso_blue$b_Associative_Trial)
d_a_b_ControlHot <- (deli_asso_blue$'b_Associative_Trial:cortControl:tempHot' + deli_asso_blue$b_Associative_Trial)
## 2) L. guichenoti
### Group = red
g_a_r_CORTCold <- guich_asso_red$b_Associative_Trial
g_a_r_ControlCold <- (guich_asso_red$'b_Associative_Trial:cortControl' + guich_asso_red$b_Associative_Trial)
g_a_r_CORTHot <- (guich_asso_red$'b_Associative_Trial:tempHot' + guich_asso_red$b_Associative_Trial)
g_a_r_ControlHot <- (guich_asso_red$'b_Associative_Trial:cortControl:tempHot' + guich_asso_red$b_Associative_Trial)
### Group = blue
g_a_b_CORTCold <- guich_asso_blue$b_Associative_Trial
g_a_b_ControlCold <- (guich_asso_blue$'b_Associative_Trial:cortControl' + guich_asso_blue$b_Associative_Trial)
g_a_b_CORTHot <- (guich_asso_blue$'b_Associative_Trial:tempHot' + guich_asso_blue$b_Associative_Trial)
g_a_b_ControlHot <- (guich_asso_blue$'b_Associative_Trial:cortControl:tempHot' + guich_asso_blue$b_Associative_Trial)
```

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task
## 1) L. delicata
### Group = red
d_r_r_CORTCold <- deli_rev_red$b_trial_reversal
d_r_r_ControlCold <- (deli_rev_red$'b_trial_reversal:cortControl' + deli_rev_red$b_trial_reversal)
d_r_r_CORTHot <- (deli_rev_red$'b_trial_reversal:tempHot' + deli_rev_red$b_trial_reversal)
d_r_r_ControlHot <- (deli_rev_red$'b_trial_reversal:cortControl:tempHot' + deli_rev_red$b_trial_reversal)
### Group = blue
d_r_b_CORTCold <- deli_rev_blue$b_trial_reversal
d_r_b_ControlCold <- (deli_rev_blue$'b_trial_reversal:cortControl' + deli_rev_blue$b_trial_reversal)
d_r_b_CORTHot <- (deli_rev_blue$'b_trial_reversal:tempHot' + deli_rev_blue$b_trial_reversal)
d_r_b_ControlHot <- (deli_rev_blue$'b_trial_reversal:cortControl:tempHot' + deli_rev_blue$b_trial_reversal)
## 2) L. guichenoti
### Group = red
g_r_r_CORTCold <- guich_rev_red$b_trial_reversal
g_r_r_ControlCold <- (guich_rev_red$'b_trial_reversal:cortControl' + guich_rev_red$b_trial_reversal)
g_r_r_CORTHot <- (guich_rev_red$'b_trial_reversal:tempHot' + guich_rev_red$b_trial_reversal)
g_r_r_ControlHot <- (guich_rev_red$'b_trial_reversal:cortControl:tempHot' + guich_rev_red$b_trial_reversal)
### Group = blue
g_r_b_CORTCold <- guich_rev_blue$b_trial_reversal
g_r_b_ControlCold <- (guich_rev_blue$'b_trial_reversal:cortControl' + guich_rev_blue$b_trial_reversal)
g_r_b_CORTHot <- (guich_rev_blue$'b_trial_reversal:tempHot' + guich_rev_blue$b_trial_reversal)
g_r_b_ControlHot <- (guich_rev_blue$'b_trial_reversal:cortControl:tempHot' + guich_rev_blue$b_trial_reversal)
```

```{r, resultsRev}
